Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-08 talk/index.Rmd
changed font mermaid diagram
changed size mermaid diagram
added participant flow chart (and changed experimental design diagram once again)

```{r, echo=FALSE, fig.align='center', out.width='80%', fig.retina=3}
knitr::include_graphics("images/mermaid.png")
```

@@

>>>>

```{r, echo=FALSE, fig.align='center', out.width='95%', fig.retina=3}
knitr::include_graphics("images/mermaid.png")
```

.center[

@@

# Participants

```{r, echo = FALSE, fig.retina=3, fig.align='center', out.width='110%'}
knitr::include_graphics("images/participants.png")
```
